A Meta-analysis of Longevity Estimates of Mosquito Vectors of Disease: Additional Methods

### 2020-01-30 writeUp/supplementary_materials_methods.tex
updated POA

For the species-level analyses, there were, hence, $n=223$ observations for Africa across 4 species; $n=141$ observations for the Americas across 6 species; and $n=214$ observations for Asia across 8 species. For the complex-level analyses, there were, hence, $n=757$ observations for Africa across 3 groups; $n=77$ observations for the Americas across 3 groups; and $n=455$ observations for Asia across 11 groups. For the continent-level and overall analyses, there were $n=1490$ observations across Africa ($n=778$), the Americas ($n=163$) and Asia ($n=549$).

>>>>

For the species-level analyses, there were, hence, $n=223$ observations for Africa across 4 species; $n=141$ observations for the Americas across 6 species; and $n=214$ observations for Asia across 8 species. For the complex-level analyses, there were, hence, $n=778$ observations for Africa across 4 groups; $n=77$ observations for the Americas across 3 groups; and $n=455$ observations for Asia across 11 groups. For the continent-level and overall analyses, there were $n=1490$ observations across Africa ($n=778$), the Americas ($n=163$) and Asia ($n=549$).
